Spitzer, Gaia and the Potential of the Milky Way

### 2013-06-24 docs/paper1/paper.tex
updated references

The distance of the stream has been estimated from photometric surveys \citep[e.g.,][]{martinezdelgado2004} and gradients in radial velocities and metallicity measured with follow-up spectroscopy \citep[e.g.,][]{vivas2005, keller2010}.

(e.g., Keller et al. 2010, ApJ, 720, 940).
%\citep{majewski04,martinez04,bellazzini06,chou07,chou10,keller10,carlin12}.
%These rich data sets have inspired equally rich interpretations of Sgr debris
% (e.g.,  Johnston et al. 1999, AJ, 118, 1719; Helmi, 2004, ApJL, 610, L97; Law et al. 2005, ApJ, 619, 807; Fellhauer et al. 2006, ApJ, 651, 167; Law \& Majewski, 2010,
ApJ, 714, 229).
%(e.g.,  Law \& Majewski, 2010, ApJ, 714, 229 -- hereafter LM10).

Figure
\ref{sgr.fig}  illustrates results from LM10's N-body
simulation of dwarf satellite disruption along the expected Sgr orbit, with particles projected onto the plane perpendicular to the
Galactic disk containing both the Sun and Galactic center.
The simulation was run in a potential…..

>>>>

The distance of the stream has been estimated from photometric surveys
\citep[e.g.,][]{martinezdelgado2004} and gradients in radial
velocities and metallicity measured with follow-up spectroscopy
\citep[e.g.,][]{majewski2004, vivas2005, bellazzini2006, chou2007,
  chou2010, keller2010, carlin2012}. The multitude of Sgr stream data
has inspired a rich set of interpretations and models of the debris
\citep[e.g.,][]{johnston1999, helmi2004, law2005, fellhauer2006,
  law2010}.

Figure \ref{fig:lm10} illustrates results from the \cite[][; hereafter
  LM10]{law2010} N-body simulation of dwarf satellite disruption along
the expected Sgr orbit, with particles projected onto the plane
perpendicular to the Galactic disk containing both the Sun and
Galactic center.  The simulation was run in a potential…..
